\documentclass[12pt]{article}
\usepackage[margin=.8in]{geometry}
\usepackage{parskip}

\title{Ripieno}
\author{Lara Janecka---Eric Pemberton---Josh Netterfield---Nik Klassen---Tyler Babaran---Kevin Carruthers}
\date{June 19th, 2014}

\begin{document}
\maketitle
Section: 106\\
Instructor: Mark Spielmacher

\section{Ripieno}
\subsection{Description}
Ripieno is a music notation program for writing and sharing sheet music. It's a social platform which allows composers to collaborate and build music together.

Ripieno is simple and easy-to-use, and supports all standard music notation formats. Anyone can sign up for Ripieno and start producing high-quality music in minutes.

\subsection{Stakeholder}
Composers of all skill levels in both professional and non-professional settings will benefit from Ripieno. Whether they produce music for a living or simply for fun, Ripieno will make their lives easier.

Furthermore, Ripieno can be used in schools by educators to provide high-quality teaching experiences to students of all ages as well as by the students themselves to explore music for themselves.

\subsection{Why Ripieno is Useful}
{\bf Creation}: Ripieno makes it easy to create and transcribe sheet music. Instead of poring over scores with every instrument in your band and dealing with more paper than you can carry, Ripieno lets you edit each instrument individually or together, work on your composition from anywhere in the world, and have access to industry-leading notational functionality.

{\bf Sharing}: Ripieno lets you share your content to everyone, everywhere, at a click of a button. Whether you're sharing with other composers, sending your sheet music to musicians, or simply showing your friends, Ripieno makes everything simple.

{\bf Collaborating}: With Ripieno, you'll never need to schedule meetings with all of your collaborators ever again. So long as they're online, Ripieno let's you all work together---in real time! Watch your collaborators' changes as they're made, discuss potential melodies in the live chat, or listen to an orchestral-quality rendering of your work.

\subsection{Our Product}
Ripieno is a fully functional web application. Simply point your web browser to www.ripieno.io and try Ripieno for yourself.

\subsection{Our Group}
Every member in our group is a highly-trained programmer dedicated to solving this problem. Ripieno is in a closed beta stage and will soon be ready for release.

\end{document}
